03_limma_pit

### 2019-03-19 scripts/03_limma_pit.Rmd
rename to change order
copy paste to function

---
title: "02_limma_vomm_pit"
output: md_document
---

@@

	         MP_CB = male.pituitary.control - male.pituitary.bldg,
	         MP_BL = male.pituitary.bldg - male.pituitary.lay,
	         MP_Li3 = male.pituitary.lay - male.pituitary.inc.d3,
	         MP_i39 = male.pituitary.inc.d3 - male.pituitary.inc.d9,
	         MP_i917 = male.pituitary.inc.d9 - male.pituitary.inc.d17,
	         MP_i17H = male.pituitary.inc.d17 - male.pituitary.hatch,
	         MP_H5 = male.pituitary.hatch -  male.pituitary.n5,
	         MP_n59 = male.pituitary.n5 - male.pituitary.n9,
	         MP_n9C = male.pituitary.n9 - male.pituitary.control,
levels=parentaldesign)

# female comparisons
cont <- "FP_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_CB', frame.plot=F)

cont <- "FP_BL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_BL', frame.plot=F)

cont <- "FP_Li3"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_Li3', frame.plot=F)

cont <- "FP_i39"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_i39', frame.plot=F)

cont <- "FP_i917"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_i917', frame.plot=F)

cont <- "FP_i17H"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_i17H', frame.plot=F)

cont <- "FP_H5"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_H5', frame.plot=F)

cont <- "FP_n59"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_n59', frame.plot=F)

cont <- "FP_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_n9C', frame.plot=F)

## male comparisons

cont <- "MP_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_CB', frame.plot=F)

cont <- "MP_BL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_BL', frame.plot=F)

cont <- "MP_Li3"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_Li3', frame.plot=F)

cont <- "MP_i39"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i39', frame.plot=F)

cont <- "MP_i917"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i917', frame.plot=F)

cont <- "MP_i17H"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i17H', frame.plot=F)

cont <- "MP_H5"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_H5', frame.plot=F)

cont <- "MP_n59"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_n59', frame.plot=F)

cont <- "MP_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_n9C', frame.plot=F)

>>>>

---
title: "03_limma_pit"
output: md_document
---

@@

	         MP_CB = male.pituitary.control - male.pituitary.bldg,
	         MP_BL = male.pituitary.bldg - male.pituitary.lay,
	         MP_Li3 = male.pituitary.lay - male.pituitary.inc.d3,
	         MP_i39 = male.pituitary.inc.d3 - male.pituitary.inc.d9,
	         MP_i917 = male.pituitary.inc.d9 - male.pituitary.inc.d17,
	         MP_i17H = male.pituitary.inc.d17 - male.pituitary.hatch,
	         MP_H5 = male.pituitary.hatch -  male.pituitary.n5,
	         MP_n59 = male.pituitary.n5 - male.pituitary.n9,
	         MP_n9C = male.pituitary.n9 - male.pituitary.control,

	         FP_n9B = female.pituitary.n9 - female.pituitary.bldg,
	         MP_n9B = male.pituitary.n9 - male.pituitary.bldg,
levels=parentaldesign)

mycontrasts <- c("FP_CB", "FP_BL", "FP_Li3", "FP_i39", "FP_i917", "FP_i17H", "FP_H5", "FP_n59", "FP_n9C",
                 "MP_CB", "MP_BL", "MP_Li3", "MP_i39", "MP_i917", "MP_i17H", "MP_H5", "MP_n59", "MP_n9C",
                 "FP_n9B", "MP_n9B")

printplotcontrasts <- function(whichcontrast){
  cont <- whichcontrast
  summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
  return(kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1))
  return(plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main=whichcontrast, frame.plot=F))
}

for(i in mycontrasts){
  printplotcontrasts(i)
}
